Nested Stochastic Block Models Applied to the Analysis of Single Cell Data

### 2021-04-27 supplementary.tex
added figure S6

\documentclass[11pt, titlepage, twoside]{article}
\usepackage[top=20mm, bottom=20mm, left=20mm, right=20mm]{geometry}
\geometry{a4paper}
\geometry{portrait}
\usepackage[utf8]{inputenc}	% Comment out for xelatex; must use with pdflatex
\usepackage[T1]{fontenc}
\usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{fontspec}
\usepackage{epstopdf}
\usepackage{float}
\usepackage[hang]{footmisc}
\usepackage{endnotes}
\usepackage{listingsutf8}
%\restylefloat{table}
\usepackage{xcolor}
\usepackage{colortbl}
%\usepackage{booktabs}
\usepackage{tabu}
\usepackage{caption}
\usepackage{textcomp}
\usepackage{textgreek}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage[normalem]{ulem}
\usepackage{authblk}

@@

%\begin{figure}[htbp]
%\centering
%\includegraphics[keepaspectratio,width=\textwidth,height=0.75\textheight]{Figure_S5.png}
%\caption[]{Adjusted Rand Index between cell clusters and cell type annotation filtering data at different cutoffs of consistency. Dot size is proportional to the number of cells remaining after filtering.}\label{MPFigure:5B291ABA-427A-42BE-BC26-38E626B1B088}
%\end{figure}

>>>>

\documentclass[11pt, titlepage, twoside]{article}
\usepackage[top=20mm, bottom=20mm, left=20mm, right=20mm]{geometry}
\geometry{a4paper}
\geometry{portrait}
\usepackage[utf8]{inputenc}	% Comment out for xelatex; must use with pdflatex
\usepackage[T1]{fontenc}
\usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{fontspec}
\usepackage{epstopdf}
\usepackage{float}
\usepackage[hang]{footmisc}
\usepackage{endnotes}
\usepackage{listingsutf8}
%\restylefloat{table}
\usepackage{xcolor}
\usepackage{colortbl}
%\usepackage{booktabs}
\usepackage{tabu}
\usepackage{caption}
\usepackage{textcomp}
\usepackage{textgreek}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage[normalem]{ulem}
\usepackage{authblk}
\usepackage{xr}
\externaldocument{manuscript}

@@

\begin{figure}[htbp]
\centering
\includegraphics[keepaspectratio,width=\textwidth,height=1\textheight]{FigureOptimalLevel.png}
\caption[]{Choice of the optimal hierarchy level. Datasets analyzed for choice of the most relevant hierarchy level are represented here, from top to bottom in the same order as in Table \ref{table_optimal}. For each dataset we report the UMAP embedding coloured by the annotation given in the corresponding manuscript, the profile of modularity $Q$ at different level of the hierarchy and the UMAP embeddings coloured by the level according to $i^k$ or $i^Q$. The dashed line in modularity plots represents the modularity calculated using the annotation from the corresponding manuscripts.}\label{FigureOptimalLevel}
\end{figure}
